---
title: "Kuy Production Analysis"
author: "Raksit T. Lau-Preechathammarach"
last-updated: "9/1/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include = FALSE}
# Conversion
library(knitr)
library(kableExtra)

library(arm)        # For standardizing (Gelman 2008)
library(hqmisc)     # For semitones to Hz conversion

# Data wrangling
library(tidyverse)

# For PCA and correlations
library(FactoMineR)
library(factoextra) # Visualization
library(corrplot)

# Modeling
library(lme4)       # For mixed models
library(lmerTest)   # For mixed models
library(splines)    # b-splines for non-linear data
library(effects)    # For graphing effects
library(jtools)     # To summarize nicely for printing

# Grobs (visualize many factors)
library(gtable)
library(grid)

library(rstudioapi)

knitr::opts_chunk$set(root.dir = dirname(getActiveDocumentContext()$path),
                      cache = TRUE, cache.lazy = TRUE, message = FALSE)

##################
# MODEL FUNCTION #
##################

# Run the model and create a dataframe with predicted results
# Make dataframe for effects
make_efdf <- function(df, model, fac1 = 'TLE', fac2 = 'away', splines = 3, timepoints = 20, sd = 1.5) {

  # timepoints = # of timepoints we want to predict for
  # sd = predict at +/- sd levels of fac1 and fac2
  
  # fac2 == FALSE if we do not include away

  # To get the cutoffs
  mean_fac1 <- mean(df[[fac1]])
  sd_fac1 <- sd(df[[fac1]])
    
  # Levels for which we are estimating effects
  l <- list(
    time = 1:timepoints,
    fac1 = c(mean_fac1-sd*sd_fac1, mean_fac1+sd*sd_fac1)
  )
  
  term <- paste0('bs(time, df = ', splines, ')*register*gender*', fac1)
  
  if (fac2 != FALSE) {
    
    mean_fac2 <- mean(df[[fac2]])
    sd_fac2 <- sd(df[[fac2]])
    
    l[[fac2]] <- c(mean_fac2-sd*sd_fac2, mean_fac2+sd*sd_fac2)
    
    term <- paste0(term, '*', fac2)
    
  }
  
  names(l) <- if (fac2 == FALSE) c('time', fac1) else c('time', fac1, fac2)
  
  ef <- as.data.frame(effect(term = term,
                             xlevels = l,
                             mod = model))
  
  # Make the breaks at these levels
  if (fac2 == FALSE) { 
    ef <- mutate(ef,
                 !!fac1 := cut(ef[[fac1]],
                               breaks = c(unique(ef[[fac1]])-.0001, max(unique(ef[[fac1]]) + .0001)),
                               labels = c('less', 'greater'))
                 )
    } else {
      ef <- mutate(ef,
                   !!fac1 := cut(ef[[fac1]],
                                 breaks = c(unique(ef[[fac1]])-.0001, max(unique(ef[[fac1]]) + .0001)),
                                 labels = c('less', 'greater')),
                   !!fac2 := cut(ef[[fac2]],
                             breaks = c(unique(ef[[fac2]])-.0001, max(unique(ef[[fac2]]) + .0001)),
                             labels = c('less', 'greater'))
      )
}

  ef[[fac1]] <- factor(ef[[fac1]], levels = c('greater', 'less'))

  return(ef)

}

# ##################
# # GRAPH FUNCTION #
# ##################
# Graph function
# xmin, xmax, ymin, ymax define the min and max limits of the x and y axes
# alpha_ribbon changes how transparent the ribbon (confidence interval) is
# text_sizes changes the size of the text
#
# The t_ functions refer to the top strip (Time Away)
# The r_ functions refer to the right strip (TLE)
#   top, bottom = Rows defining top and bottom of the strip--(1 is the bottom of the whole graph)
#   left, right = Columns defining left and right of strip--(1 is the left of the whole graph)
#   stripgap = Size of gap between strip and main graph
#   size = Size of font
#   stripgap = Size of gap between strip and main graph
#   size = Size of font
#
#   rstrip_legend_gap = Size of gap between strip and legend
#   col_gap = Size of gap between strip and levels
#   raw = if TRUE, plot raw values
#   convert_semi = if TRUE, convert semitones to Hz
graph <- function(ef, meas, fac1 = 'TLE', fac1_title = 'Tonal Language Experience', 
                  fac2 = 'away', fac2_title = 'Time Away',
                  xmin = 0, xmax = 20, ymin = FALSE, ymax = FALSE, 
                  alpha_ribbon = 0.25, text_sizes = 12,
                  t_left = 5, t_right = 7, t_top = 7, t_bottom = 7, t_stripgap = 2/10, t_size = 1,
                  r_left = 11, r_right = 12, r_top = 10, r_bottom = 12, r_stripgap = 2/10, r_size = 1, r_strippos = 10,
                  rstrip_legend_gap = 5, col_gap = 10,
                  gg_title = '', gg_titlesize = 20,
                  raw = FALSE, convert_semi = FALSE) {
  
  # Dictionary to map measurements to labels
  measure_text <- c('f0', 'H1*-H2*', 'H1*(-An*)', 'CPP', 'F1')
  names(measure_text) <- c('f0_semitones', 'H1H2c', 'H1Anc_PC', 'CPP', 'F1_semitones')
  
  # Label for y-axis
  ylabel <- c('Estimated', measure_text[meas])
  
  if (raw == TRUE) {
      
      if (meas %in% c('f0_semitones', 'F1_semitones')) {
        
        ifelse(convert_semi, ylabel <- c(ylabel, '(Hz)'), ylabel <- c(ylabel, '(semitones)'))
        
      } else {
        
        ylabel <- c(ylabel, '(dB)')
        
      }
   
  } else {
    
      ylabel <- c(ylabel, '(scaled)')
    
  }
  
  y <- ifelse(raw, 'fit_raw', 'fit')
  lower_y <- ifelse(raw, 'lower_raw', 'lower')
  upper_y <- ifelse(raw, 'upper_raw', 'upper')
  
  if ((meas %in% c('f0_semitones', 'F1_semitones')) & (convert_semi == TRUE)) {
    
    y <- paste0(y, '_Hz')
    lower_y <- paste0(lower_y, '_Hz')
    upper_y <- paste0(upper_y, '_Hz')
      
  }
  
  # Set up the basic plot
  p <- ggplot(ef, aes_string(x = 'time', y = y, color = 'register')) +
    geom_line() +
    geom_ribbon(aes_string(ymin = lower_y, ymax = upper_y, fill = 'register'), alpha = alpha_ribbon, color = NA) +
    xlim(xmin,xmax)
  
  if ((ymin != FALSE) || (ymax != FALSE)) {
    p <- p + ylim(ymin, ymax)
  }
  
  p <- p + 
    labs(x = 'Normalized Time',
         y = paste(ylabel, collapse = ' ')) +
    facet_grid(reformulate(fac2, fac1)) +
    ggtitle(gg_title) +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5,
                                    size = gg_titlesize, face = 'bold'),
          text = element_text(size = text_sizes),
          legend.position = 'none') +
    scale_fill_brewer(name = 'Register', palette = 'Set1') +
    scale_color_brewer(name = 'Register', palette = 'Set1')
  
  #############################
  # Now add strips with grobs #
  #############################
  z <- ggplotGrob(p)
  
  #  New strip at the top
  z <- gtable_add_rows(z, z$height[7], pos = 6)  # New row added below row 6
  
  z <- gtable_add_grob(z,
                       list(rectGrob(gp = gpar(col = NA, fill = "gray85", size = .5)),
                            textGrob(fac2_title,
                                     gp = gpar(cex = t_size, fontface = 'bold', col = "black"))),
                       t=t_top, l=t_left, b=t_bottom, r=t_right, name = c("a", "b"))
  
  # Add small gap between strips - below row 6
  z <- gtable_add_rows(z, unit(t_stripgap, "line"), 7)
  
  #########
  
  #  New strip to the right
  z <- gtable_add_cols(z, unit(rstrip_legend_gap, 'pt'), pos = r_strippos)
  
  # Check the layout
  # New strip spans rows 7 to 11
  z <- gtable_add_grob(z,
                       list(rectGrob(gp = gpar(col = NA, fill = "gray85", size = .5)),
                            textGrob(fac1_title, rot = -90,
                                     gp = gpar(cex = r_size, fontface = 'bold', col = "black"))),
                       t=r_top, l=r_left, b=r_bottom, r=r_right, name = c("a", "b"))
  
  # Add small gap between strips - to the right of column 6
  z <- gtable_add_cols(z, unit(r_stripgap, "line"), col_gap)
  
  return(z)
  
}
```

# Read in data and scale for comparability

```{r readdata, cache=TRUE, message=FALSE}
df <- read_csv('../0_data/kuy-production-clean.csv')

# Speaker number is not on a scale
df$sp <- as.character(df$sp)

# Vowel heights
heights <- c('high', 'high', 'mid-high', 'mid-high', 'mid-low', 'low', 'low')
names(heights) <- c('ii', 'uu', 'ee', 'oo', 'EE', 'a', 'A')

df$vheight <- heights[df$vowelqual]

# Rescale the means by speaker
for (meas in c('f0', 'f0_semitones', 'H1c', 'H1H2c', 'H1A1c', 'H1A2c', 'H1A3c', 'CPP', 'F1', 'F1_semitones')) {
  
  varname <- paste(meas, 'scaled', sep = '_')

  # If F1, scale by height too
  if (meas %in% c('F1', 'F1_semitones')) {

    df <- as.data.frame(df %>%
                          group_by(sp, vheight) %>%
                          mutate(!!varname := arm::rescale(get(meas))) %>%
                          ungroup())
  } else {

  df <- as.data.frame(df %>%
                        group_by(sp) %>%
                        mutate(!!varname := arm::rescale(get(meas))) %>%
                        ungroup())

  }
  
}
```

```{r rmd, include = FALSE}
# If Rmd is true, all info will be presented for knitting

rmd <- TRUE

measures <- c('F0_semitones', 'H1H2c', 'H1Anc_PC', 'CPP', 'F1_semitones')
```

# Run PCA on acoustic correlates of voice quality

```{r pca, cache = TRUE}
# Subset for PCA
pca_df <- df %>% dplyr::select(H1c_scaled, H1H2c_scaled, H1A1c_scaled, H1A2c_scaled, H1A3c_scaled, CPP_scaled)

# Change column names
colnames(pca_df) <- c('H1*', 'H1* - H2*', 'H1* - A1*', 'H1* - A2*', 'H1* - A3*', 'CPP')

# Look at correlations (unncomment commands below if want to produce graphics)
#bitmap('vqual-corr.tiff', height = 8, width = 8, units = 'in', type = 'tifflzw', res = 300)
#postscript("vqual-corr.eps", height = 8, width = 8, paper = 'special')
# pdf('vqual-corr.pdf', height = 8, width = 8)
corrplot(cor(pca_df), method = 'circle', diag = FALSE, type = 'upper', addCoef.col = 'black')
# dev.off()

# Run PCA
vq.pca <- PCA(pca_df, graph = FALSE, ncp = 6)

# Scree plot (unncomment commands below if want to produce graphics)
#bitmap('vqual-scree.tiff', height = 4, width = 6, units = 'in', type = 'tifflzw', res = 300)
#postscript("vqual-scree.eps", height = 4, width = 6, paper = 'special')
# pdf('vqual-scree.pdf', height = 4, width = 6)
fviz_screeplot(vq.pca, addlabels = FALSE, title = '') +
  geom_text(aes(label = round(vq.pca$eig[, 2], 2)), size = 5, hjust = 0.1, vjust = -0.5) +
  theme(text = element_text(size = 15)) +
  ylim(0,45)
# dev.off()

# Contributions to dimension 1 (unncomment commands below if want to produce graphics)
#bitmap('vqual-dim1.tiff', height = 4, width = 6, units = 'in', type = 'tifflzw', res = 300)
#postscript("vqual-dim1.eps", height = 4, width = 6, paper = 'special')
# pdf('vqual-dim1.pdf', height = 4, width = 6)
p <- fviz_contrib(vq.pca, choice = "var", title = '', axes = 1) +
  geom_text(aes(label = round(contrib, 2)), vjust = -1, size = 5) +
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15)) +
  ylim(0, 35)
p$layers[[2]] <- NULL
p
# dev.off()

```


```{r addpca, cache=TRUE}
# Add dimension 1 to data frame and rescale
df$H1Anc_PC <- vq.pca$ind$coord[, 1]
df$H1Anc_PC_scaled <- arm::rescale(df$H1Anc_PC)

# Save H1Anc_PC values for use with LDA
write.csv(df, '../0_data/kuy-production-clean.csv', row.names = FALSE)

# Also turn experiencePC to TLE (Tonal Language Experience)
# And transform years away as it is right skewed, and then scale it
dem <- read_csv('../0_data/kuy-production-dem.csv')

dem$TLE <- arm::rescale(-dem$experiencePC)
dem$away <- arm::rescale(sqrt(dem$yearsaway))

# Update demographic info
write.csv(dem, '../0_data/kuy-production-dem.csv', row.names = FALSE)

# Merge with main df for model
df <- merge(df, dem, by = 'sp')

```

# Models

### Measures
- f0: fundamental frequency (can add _semitones)
- H1H2c: H1\*-H2*
- H1Anc_PC: PC corresponding largely to H1* and H1\*-An*
- CPP: Cepstral Peak Prominence
- F1_byheight: first formant (can add _semitones before _byheight)

```{r model, cache=TRUE, include=FALSE}
models = list()

fac1 <- 'TLE'
fac2 <- 'away'
splines <- 3
randef <- '(1|sp) + (1|word)'

measures <- c('f0_semitones', 'H1H2c', 'H1Anc_PC', 'CPP', 'F1_semitones')

# Run linear regression
for (m in measures) {
  
  m_scaled <- paste0(m, '_scaled')
  
  print(paste0('Running model for ', m, '...'))
  
  models[[m]] <- lmer(as.formula(paste0(m_scaled, ' ~ bs(time, df = ', splines, ')*register*gender*', fac1, '*', fac2, ' + ', randef)), data = df, control=lmerControl(optimizer = "bobyqa"), REML = FALSE)
  
}

```

# Effects

```{r effects, cache=TRUE}
efs = list()

# Get effect df from model
for (m in measures) {
  
  print(paste0('Estimating effects for ', m, '...'))
  
  if (m %in% c('H1H2c', 'F1_semitones')) {
    efs[[m]] <- make_efdf(df = df, model = models[[m]], fac1 = fac1, fac2 = FALSE, splines = 3, timepoints = 20, sd = 1.5)
  } else {
    efs[[m]] <- make_efdf(df = df, model = models[[m]], fac1 = fac1, fac2 = fac2, splines = 3, timepoints = 20, sd = 1.5)
  }
  
}

```

# Get means and SDs for each measure

```{r meansd, cache=TRUE}
# Dictionary for summary statistics
sumstats = list()

for (m in measures) {
  
  if (m == 'F1_semitones') {
    
    sumstats[[paste0(m, '_sumstats')]] <- df %>%
    group_by(gender, sp, vheight) %>%
    summarize(mean = mean(get(m)),
              sd = sd(get(m)))
    
  } else {
    
    sumstats[[paste0(m, '_sumstats')]] <- df %>%
    group_by(gender, sp) %>%
    summarize(mean = mean(get(m)),
              sd = sd(get(m)))
  }
  
}
```

# Convert effect df scaled values back to raw

```{r converteffects, cache=TRUE}
#  mean + 2 * sd * value

est <- c('fit', 'se', 'upper', 'lower')

# Dictionary of efs for graphing
ef_graph <- list()

# We need effects for each measure for each gender
for (m in measures) {
  
  # Get ef and sumstats
  efdf <- efs[[m]]
  ssdf <- sumstats[[paste(m, 'sumstats', sep = '_')]]
  
  # If F1, we need to subset by each height
  if (m == 'F1_semitones') {
    
    for (h in c('high', 'mid-high', 'mid-low', 'low')) {
      
      # Make subsetted df for height
      subefname <- paste(c(m, h), collapse = '_')
      
      ef_graph[[subefname]] <- efdf
      
      # Transform to raw values
      ef_graph[[subefname]][paste(est, 'raw', sep = '_')] <- 
        lapply(ef_graph[[subefname]][est], function (x)
          mean(ssdf[ssdf$gender == g & ssdf$vheight == h, ]$mean) + 
          2 * mean(ssdf[ssdf$gender == g & ssdf$vheight == h, ]$sd) * x)
       
      # Transform to Hz
      ef_graph[[subefname]][paste(est, 'raw', 'Hz', sep = '_')] <-
        lapply(ef_graph[[subefname]][paste(est, 'raw', sep = '_')], function (x) st2f(x, base = 75))
      
    }
  
  } else if (m == 'H1H2c') {
    
    ef_graph[[m]] <- efdf
    
    # Transform to raw values
    ef_graph[[m]][paste(est, 'raw', sep = '_')] <- 
      lapply(ef_graph[[m]][est], function (x)
        mean(ssdf[ssdf$gender == g, ]$mean) + 
        2 * mean(ssdf[ssdf$gender == g , ]$sd) * x)
    
  } else {
  
    for (g in c('f', 'm')) {
       
        # Make subsetted df for gender
        subefname <- paste(c(m, g), collapse = '_')
        
        ef_graph[[subefname]] <- efdf[efdf$gender == g, ]
        
        # Transform to raw values
        ef_graph[[subefname]][paste(est, 'raw', sep = '_')] <- 
          lapply(ef_graph[[subefname]][est], function (x)
            mean(ssdf[ssdf$gender == g, ]$mean) + 
            2 * mean(ssdf[ssdf$gender == g , ]$sd) * x)
        
        # Transform to Hz
        ef_graph[[subefname]][paste(est, 'raw', 'Hz', sep = '_')] <- 
          lapply(ef_graph[[subefname]][paste(est, 'raw', sep = '_')], function (x) st2f(x, base = 75))
          
    }
  
  }
    
}

```

# Graph effects for 5-way interactions that are significant

```{r graph}
for (m in measures) {
  
  raw <- ifelse(m %in% c('H1Anc_PC', 'F1_semitones'), FALSE, TRUE)
  ymin <- ifelse(m %in% c('H1Anc_PC', 'F1_semitones'), -1, FALSE)
  ymax <- ifelse(m %in% c('H1Anc_PC', 'F1_semitones'), 1, FALSE)
  convert_semi <- ifelse(m == 'f0_semitones', TRUE, FALSE)
  
  if (m == 'F1_semitones') {
    
    for (h in c('high', 'mid-high', 'mid-low', 'low')) {

          print(paste(m, h, collapse = ', '))

          z <- graph(ef = ef_graph[[paste(m, h, sep = '_')]], meas = m,
               fac1 = fac1, fac1_title = 'Tonal Language Experience',
               fac2 = 'gender', fac2_title = 'Gender', gg_title = '',
               raw = raw, convert_semi = convert_semi,
               ymin = ymin, ymax = ymax,
               r_left = 11, r_right = 12, rstrip_legend_gap = 20,
               text_sizes = 18, t_size = 1.25, r_size = 1)

          pdf(paste0(m, '-', h, '.pdf'), height = 4, width = 6)
          grid.newpage()
          grid.draw(z)
          dev.off()

    }
    
  } else if (m == 'H1H2c') {
    
    print(m)
    
    z <- graph(ef = ef_graph[[m]], meas = m,
               fac1 = fac1, fac1_title = 'Tonal Language Experience',
               fac2 = 'gender', fac2_title = 'Gender', gg_title = '',
               raw = raw, convert_semi = convert_semi,
               ymin = ymin, ymax = ymax,
               r_left = 11, r_right = 12, rstrip_legend_gap = 20,
               text_sizes = 18, t_size = 1.25, r_size = 1)
  
        pdf(paste0(m, '-', g, '.pdf'), height = 4, width = 6)
        grid.newpage()
        grid.draw(z)
        dev.off()
    
  } else {
  
    for (g in c('f', 'm')) {
      
      print(paste(m, g, collapse = ', '))
    
      z <- graph(ef = ef_graph[[paste(m, g, sep = '_')]], meas = m,
             fac1 = fac1, fac1_title = 'Tonal Language Experience',
             fac2 = fac2, fac2_title = 'Time Away', gg_title = '',
             raw = raw, convert_semi = convert_semi,
             ymin = ymin, ymax = ymax,
             r_left = 11, r_right = 12, rstrip_legend_gap = 20,
             text_sizes = 18, t_size = 1.25, r_size = 1)

      pdf(paste0(m, '-', g, '.pdf'), height = 4, width = 6)
      grid.newpage()
      grid.draw(z)
      dev.off()
  
    }
  
  }

}



```
# Summarize models
Choose a model in the models list to summarize

```{r summodel}
mod <- models$f0_semitones

rmd <- TRUE

if (rmd == TRUE) {
  for (meas in measures) {
    print(meas)
    print(kable(summ(models[[meas]])$coeftable, format = 'markdown'))
  }
} else {
  print(meas)
  print(kable(summ(mod)$coeftable, format = 'markdown', digits = 2))
}

```

# Summarize trajectory differences
Choose 
- measure: f0_semitones, H1H2c, H1Anc_PC, CPP, F1_semitones
- gender: f, m
- optionally vowel height: high, mid-high, mid-low, low
Must add _ before gender and height. If not F1_semitones, this should be blank: ''

```{r convertraw, warning=FALSE}
# m <- 'H1H2c'
# g <- '_m'
# h <- ''

if (rmd == TRUE) {
  for (m in measures) {
    
      raw <- ifelse(substr(m, 0, 2) %in% c('f0', 'F1'), 'fit_raw_Hz', 'fit_raw')
      
      if (grepl('F1', m, fixed = TRUE)) {
        for (h in c('high', 'mid-high', 'mid-low', 'low')) {
          raw <- ifelse(substr(m, 0, 2) %in% c('f0', 'F1'), 'fit_raw_Hz', 'fit_raw')
          
          sumest <- ef_graph[[paste(m, h, sep = '_')]] %>%
          group_by(gender, TLE, register) %>%
          summarize(mean_scaled = mean(fit),
                    mean_raw = mean(get(raw)))
          
          sumdiff <- sumest[sumest$register == 'modal', ]
          
          sumdiff$mbdiff_raw <- sumdiff$mean_raw - sumest[sumest$register == 'breathy', ]$mean_raw
          
          sumdiff$mbdiff_scaled <- sumdiff$mean_scaled - sumest[sumest$register == 'breathy', ]$mean_scaled
          
          sumdiff <- sumdiff[ , !names(sumdiff) %in% c('register', 'mean_scaled', 'mean_raw')]
          
          print(paste(m, h, sep = ', '))
          print(kable(sumdiff, format = 'markdown', digits = 2))
        }
      } else if (m == 'H1H2c') {
        
          sumest <- ef_graph[[paste(m, sep = '_')]] %>%
              group_by(gender, TLE, register) %>%
              summarize(mean_scaled = mean(fit),
                        mean_raw = mean(get(raw)))
          
          sumdiff <- sumest[sumest$register == 'modal', ]
          
          sumdiff$mbdiff_raw <- sumdiff$mean_raw - sumest[sumest$register == 'breathy', ]$mean_raw
          
          sumdiff$mbdiff_scaled <- sumdiff$mean_scaled - sumest[sumest$register == 'breathy', ]$mean_scaled
          
          sumdiff <- sumdiff[ , !names(sumdiff) %in% c('register', 'mean_scaled', 'mean_raw')]
          
          print(m)
          print(kable(sumdiff, format = 'markdown', digits = 2))
          
      } else {
        
        for (g in c('f', 'm')) {
        
          sumest <- ef_graph[[paste(m, g, sep = '_')]] %>%
          group_by(gender, TLE, away, register) %>%
          summarize(mean_scaled = mean(fit),
              mean_raw = mean(get(raw)))
          
          sumdiff <- sumest[sumest$register == 'modal', ]
        
          sumdiff$mbdiff_raw <- sumdiff$mean_raw - sumest[sumest$register == 'breathy', ]$mean_raw
          
          sumdiff$mbdiff_scaled <- sumdiff$mean_scaled - sumest[sumest$register == 'breathy', ]$mean_scaled
          
          sumdiff <- sumdiff[ , !names(sumdiff) %in% c('register', 'mean_scaled', 'mean_raw')]
  
          print(paste(m, g, sep = ', '))        
          print(kable(sumdiff, format = 'markdown', digits = 2))
          
      }
        
      sumdiff <- sumest[sumest$register == 'modal', ]
      
      sumdiff$mbdiff_raw <- sumdiff$mean_raw - sumest[sumest$register == 'breathy', ]$mean_raw
      
      sumdiff$mbdiff_scaled <- sumdiff$mean_scaled - sumest[sumest$register == 'breathy', ]$mean_scaled
      
      sumdiff <- sumdiff[ , !names(sumdiff) %in% c('register', 'mean_scaled', 'mean_raw')]

      print(paste(m, g, sep = ', '))        
      print(kable(sumdiff, format = 'markdown', digits = 2))
  
    }
  }
} else {
  raw <- ifelse(substr(m, 0, 2) %in% c('f0', 'F1'), 'fit_raw_Hz', 'fit_raw')
  
  # Consider height if F1
  if (grepl('F1', m, fixed = TRUE)) {
    sumest <- ef_graph[[paste0(m, g, h)]] %>%
      group_by(gender, TLE, register) %>%
      summarize(mean_scaled = mean(fit),
                mean_raw = mean(get(raw)))
  } else if (m == 'H1H2c') {
    sumest <- ef_graph[[paste0(m, g)]] %>%
      group_by(gender, TLE, register) %>%
      summarize(mean_scaled = mean(fit),
                mean_raw = mean(get(raw)))
  } else {
    sumest <- ef_graph[[paste0(m, g)]] %>%
      group_by(gender, TLE, away, register) %>%
      summarize(mean_scaled = mean(fit),
                mean_raw = mean(get(raw)))
  }
  
  sumdiff <- sumest[sumest$register == 'modal', ]
  
  sumdiff$mbdiff_raw <- sumdiff$mean_raw - sumest[sumest$register == 'breathy', ]$mean_raw
  
  sumdiff$mbdiff_scaled <- sumdiff$mean_scaled - sumest[sumest$register == 'breathy', ]$mean_scaled
  
  sumdiff <- sumdiff[ , !names(sumdiff) %in% c('register', 'mean_scaled', 'mean_raw')]
  
  print(paste(m, g, h, sep = ', '))
  print(kable(sumdiff, format = 'markdown', digits = 2))
}
```
